Interactive dashboard to monitor the COVID-19 outbreak

### 2022-04-20 manuscript_covid19dashboard.Rmd
Updated the paper

>>>>

Table 5 provides an overview of methods that have been used to visualize data.

**Table 5: Data visualization approaches used to visualize data**

| **Data**|**Type of graphics**| 
|:-------------------|:----------------|
|Daily COVID-19 confirmed          |Time series plots \hfill\break
|Daily COVID-19 recovered cases by time         |Time series plots \hfill\break
|Daily COVID-19 death cases by time         |Time series plots \hfill\break
|Total COVID-19 confirmed cases by time and wave         |Time series plots annotated with vertical lines to denote significant milestones \hfill\break
|Total COVID-19 death cases by time and wave         | Histogram \hfill\break
|Distribution of COVID-19 patients by districts        | Tile map, Choropleth maps, Dorling Cartogram, heatmaps \hfill\break
|Total vaccination by first dose and second dose        | Time series plot \hfill\break
|Total administrated does by vaccine name       | Stacked bar chart \hfill\break
|Total administrated does by vaccine name       | Stacked bar chart \hfill\break
|Total administrated does by vaccine name       | Stacked bar chart \hfill\break
|Comparison of cases with in Sri Lanka with Top 10 countries       | Cummulative cases by time, Log of cummulative cases by time, stacked bar chart \hfill\break
|Spread of COVID-19 around the world      | Choropleth maps \hfill\break
